---
title: "Visualisations"
output: html_document

---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r 002, librarys, data loading, message=FALSE,,echo=FALSE}

library(Seurat)
#library(SeuratData)
library(ggplot2)
library(patchwork)
library(dplyr)
library(rmarkdown)
library(ggrepel)
library(readxl)
library(viridis)
library(cowplot)

```



```{r 003, data loading, message=FALSE,echo=FALSE}
load("spat_merge_all_lognorm.RData")
load("spat_merge_all.RData")
```




# Figure 3

## Figure 3b) umap 

```{r 004,  message=FALSE, echo=FALSE, warning=FALSE,fig.width = 10,fig.height = 8,dev='svg'}

DimPlot(spat.merge.all, reduction = "umap", group.by = c("ident"),label = TRUE)


```



# Figure S7

## Figure S7B spatial cluster


```{r 005,  message=FALSE, echo=FALSE, warning=FALSE,fig.width = 10,fig.height = 8,dev='svg'}

SpatialDimPlot(spat_merge_log_norm, images ="slice1")

SpatialDimPlot(spat_merge_log_norm, images ="slice1_B2")

SpatialDimPlot(spat_merge_log_norm, images ="slice1_C2")

SpatialDimPlot(spat_merge_log_norm,  images ="slice1_D2")


```

## Figure S7C spatial cluster (single cluster visualisation) 

```{r 006, dimreduction,  message=FALSE, ,width = 8,fig.height = 10}


#Decision for subsetting 
cluster123A2<-SpatialDimPlot(spat.merge.all, cells.highlight = CellsByIdentities(object = spat.merge.all, idents = c(0, 1, 2)), facet.highlight = TRUE, ncol = 3, images ="slice1")
cluster123B2<-SpatialDimPlot(spat.merge.all, cells.highlight = CellsByIdentities(object = spat.merge.all, idents = c(0, 1, 2)), facet.highlight = TRUE, ncol = 3, images ="slice1_B2")
cluster123C2<-SpatialDimPlot(spat.merge.all, cells.highlight = CellsByIdentities(object = spat.merge.all, idents = c(0, 1, 2)), facet.highlight = TRUE, ncol = 3, images ="slice1_C2")
cluster123D2<-SpatialDimPlot(spat.merge.all, cells.highlight = CellsByIdentities(object = spat.merge.all, idents = c(0, 1, 2)), facet.highlight = TRUE, ncol = 3, images ="slice1_D2")

wrap_plots(cluster123A2, cluster123B2, cluster123C2, cluster123D2,nrow=4)

cluster345A2<-SpatialDimPlot(spat.merge.all, cells.highlight = CellsByIdentities(object = spat.merge.all, idents = c(3, 4, 5)), facet.highlight = TRUE, ncol = 3, images ="slice1")
cluster345B2<-SpatialDimPlot(spat.merge.all, cells.highlight = CellsByIdentities(object = spat.merge.all, idents = c(3, 4, 5)), facet.highlight = TRUE, ncol = 3, images ="slice1_B2")
cluster345C2<-SpatialDimPlot(spat.merge.all, cells.highlight = CellsByIdentities(object = spat.merge.all, idents = c(3, 4, 5)), facet.highlight = TRUE, ncol = 3, images ="slice1_C2")
cluster345D2<-SpatialDimPlot(spat.merge.all, cells.highlight = CellsByIdentities(object = spat.merge.all, idents = c(3, 4, 5)), facet.highlight = TRUE, ncol = 3, images ="slice1_D2")

wrap_plots(cluster345A2, cluster345B2, cluster345C2, cluster345D2,nrow=4)


cluster678A2<-SpatialDimPlot(spat.merge.all, cells.highlight = CellsByIdentities(object = spat.merge.all, idents = c(6, 7, 8)), facet.highlight = TRUE, ncol = 3, images ="slice1")
cluster678B2<-SpatialDimPlot(spat.merge.all, cells.highlight = CellsByIdentities(object = spat.merge.all, idents = c(6, 7, 8)), facet.highlight = TRUE, ncol = 3, images ="slice1_B2")
cluster678C2<-SpatialDimPlot(spat.merge.all, cells.highlight = CellsByIdentities(object = spat.merge.all, idents = c(6, 7, 8)), facet.highlight = TRUE, ncol = 3, images ="slice1_C2")
cluster678D2<-SpatialDimPlot(spat.merge.all, cells.highlight = CellsByIdentities(object = spat.merge.all, idents = c(6, 7, 8)), facet.highlight = TRUE, ncol = 3, images ="slice1_D2")

wrap_plots(cluster678A2, cluster678B2, cluster678C2, cluster678D2, nrow=4)

cluster91011A2<-SpatialDimPlot(spat.merge.all, cells.highlight = CellsByIdentities(object = spat.merge.all, idents = c(9, 10, 11)), facet.highlight = TRUE, ncol = 3, images ="slice1")
cluster91011B2<-SpatialDimPlot(spat.merge.all, cells.highlight = CellsByIdentities(object = spat.merge.all, idents = c(9, 10, 11)), facet.highlight = TRUE, ncol = 3, images ="slice1_B2")
cluster91011C2<-SpatialDimPlot(spat.merge.all, cells.highlight = CellsByIdentities(object = spat.merge.all, idents = c(9, 10, 11)), facet.highlight = TRUE, ncol = 3, images ="slice1_C2")
cluster91011D2<-SpatialDimPlot(spat.merge.all, cells.highlight = CellsByIdentities(object = spat.merge.all, idents = c(9, 10, 11)), facet.highlight = TRUE, ncol = 3, images ="slice1_D2")

wrap_plots(cluster91011A2, cluster91011B2, cluster91011C2, cluster91011D2, nrow=4)

# cluster121314A2<-SpatialDimPlot(spat.merge.all, cells.highlight = CellsByIdentities(object = spat.merge.all, idents = c(12, 13, 14)), facet.highlight = TRUE, ncol = 3, images ="slice1")
# cluster121314B2<-SpatialDimPlot(spat.merge.all, cells.highlight = CellsByIdentities(object = spat.merge.all, idents = c(12, 13, 14)), facet.highlight = TRUE, ncol = 3, images ="slice1_B2")
# cluster121314C2<-SpatialDimPlot(spat.merge.all, cells.highlight = CellsByIdentities(object = spat.merge.all, idents = c(12, 13, 14)), facet.highlight = TRUE, ncol = 3, images ="slice1_C2")
# cluster121314D2<-SpatialDimPlot(spat.merge.all, cells.highlight = CellsByIdentities(object = spat.merge.all, idents = c(12, 13, 14)), facet.highlight = TRUE, ncol = 3, images ="slice1_D2")

#wrap_plots(cluster121314A2, cluster121314B2, cluster121314C2, cluster121314D2, nrow=4)

# cluster12A2<-SpatialDimPlot(spat.merge.all, cells.highlight = CellsByIdentities(object = spat.merge.all, idents = c(12)), facet.highlight = TRUE, ncol = 1, images ="slice1")
# cluster12B2<-SpatialDimPlot(spat.merge.all, cells.highlight = CellsByIdentities(object = spat.merge.all, idents = c(12)), facet.highlight = TRUE, ncol = 1, images ="slice1_B2")
# cluster12C2<-SpatialDimPlot(spat.merge.all, cells.highlight = CellsByIdentities(object = spat.merge.all, idents = c(12)), facet.highlight = TRUE, ncol = 1, images ="slice1_C2")
# cluster12D2<-SpatialDimPlot(spat.merge.all, cells.highlight = CellsByIdentities(object = spat.merge.all, idents = c(12)), facet.highlight = TRUE, ncol = 1, images ="slice1_D2")
# 
# wrap_plots(cluster91011A2, cluster91011B2, cluster91011C2, cluster91011D2, nrow=4)

```

##Gene counts

```{r 007,  message=FALSE,warning=FALSE,echo=FALSE,fig.width = 25,fig.height = 6, dev='svg'}
# pq1<-SpatialFeaturePlot(spat_merge_log_norm, features = "nFeature_Spatial", images ="slice1")+ theme(legend.position = "right")
# pq2<-SpatialFeaturePlot(spat_merge_log_norm, features = "nFeature_Spatial",  images ="slice1_B2")+ theme(legend.position = "right")
# pq3<-SpatialFeaturePlot(spat_merge_log_norm, features = "nFeature_Spatial",  images ="slice1_C2")+ theme(legend.position = "right")
# pq4<-SpatialFeaturePlot(spat_merge_log_norm, features = "nFeature_Spatial",  images ="slice1_D2")+ theme(legend.position = "right")
# 
# wrap_plots(pq1, pq2, pq3, pq4, nrow=1)

```


##UMI counts

```{r 008,  message=FALSE,warning=FALSE,echo=FALSE,fig.width = 25,fig.height = 6, dev='svg'}
# pq1<-SpatialFeaturePlot(spat_merge_log_norm, features = "nCount_Spatial", images ="slice1")+ theme(legend.position = "right")
# pq2<-SpatialFeaturePlot(spat_merge_log_norm, features = "nCount_Spatial",  images ="slice1_B2")+ theme(legend.position = "right")
# pq3<-SpatialFeaturePlot(spat_merge_log_norm, features = "nCount_Spatial",  images ="slice1_C2")+ theme(legend.position = "right")
# pq4<-SpatialFeaturePlot(spat_merge_log_norm, features = "nCount_Spatial",  images ="slice1_D2")+ theme(legend.position = "right")
# 
# wrap_plots(pq1, pq2, pq3, pq4, nrow=1)

```


## Figure S7D&E Anatomical layers & Fenale states

```{r 009,  message=FALSE, echo=FALSE, warning=FALSE,fig.width = 10,fig.height = 8,dev='svg'}

DimPlot(spat_merge_log_norm, reduction = "umap", group.by = c("ident"),label = TRUE)
DimPlot(spat_merge_log_norm, reduction = "umap", group.by = c("orig.ident"))

```












## Figure S7F Vlnplot Gene count

```{r 010,  message=FALSE,warning=FALSE,echo=FALSE,fig.width = 15,fig.height = 10, dev='svg'}
VlnPlot(spat_merge_log_norm, features = "nFeature_Spatial", pt.size = 0.1, group.by = "orig.ident") +  geom_boxplot(width=0.1, fill="white")


```

## Figure S7F Vlnplot UMI count

```{r 011,  message=FALSE,warning=FALSE,echo=FALSE,fig.width = 15,fig.height = 10, dev='svg'}
VlnPlot(spat_merge_log_norm, features = "nCount_Spatial", pt.size = 0.1, group.by = "orig.ident") +  geom_boxplot(width=0.1, fill="white")

```

## Figure S7G Heatmap top10


```{r 012,  message=FALSE, echo=FALSE, warning=FALSE,fig.width = 15,fig.height = 12,dev='svg'}

DefaultAssay(spat.merge.all) <- "SCT"
markers <- FindAllMarkers(spat.merge.all, only.pos = TRUE, min.pct = 0.25, logfc.threshold = 0.25)
markers %>%
    group_by(cluster) %>%
    top_n(n = 10, wt = avg_log2FC) -> top10

DoHeatmap(spat.merge.all, features = top10$gene)

```

## Figure S7H in paper done by web app

# S7H) no cutoff ,cutoff from paper and q95

cutoff 3/Nrgn

```{r 013,  message=FALSE, echo=FALSE,fig.width = 10,fig.height = 6, warning=FALSE, dev='svg'}

# SpatialFeaturePlot(object = spat_merge_log_norm,features ="Nrgn")
# SpatialFeaturePlot(object = spat_merge_log_norm,features ="Nrgn",max.cutoff = 3)
# SpatialFeaturePlot(object = spat_merge_log_norm,features ="Nrgn",max.cutoff = 'q95')

```

cutoff 4/Pcp4


```{r 014,  message=FALSE, echo=FALSE,fig.width = 10,fig.height = 6, warning=FALSE, dev='svg'}

# SpatialFeaturePlot(object = spat_merge_log_norm,features ="Pcp4")
# SpatialFeaturePlot(object = spat_merge_log_norm,features ="Pcp4",max.cutoff = 4)
# SpatialFeaturePlot(object = spat_merge_log_norm,features ="Pcp4",max.cutoff = 'q95')

```


cutoff 3/Uchl1

```{r 015,  message=FALSE, echo=FALSE,fig.width = 10,fig.height = 6, warning=FALSE, dev='svg'}

# SpatialFeaturePlot(object = spat_merge_log_norm,features ="Uchl1")
# SpatialFeaturePlot(object = spat_merge_log_norm,features ="Uchl1",max.cutoff = 3)
# SpatialFeaturePlot(object = spat_merge_log_norm,features ="Uchl1",max.cutoff = 'q95')

```

cutoff 3/Trh

```{r 016,  message=FALSE, echo=FALSE,fig.width = 10,fig.height = 6, warning=FALSE, dev='svg'}

# SpatialFeaturePlot(object = spat_merge_log_norm,features ="Trh")
# SpatialFeaturePlot(object = spat_merge_log_norm,features ="Trh",max.cutoff = 3)
# SpatialFeaturePlot(object = spat_merge_log_norm,features ="Trh",max.cutoff = 'q95')

```

cutoff 3,2/Doc2g

```{r 017,  message=FALSE, echo=FALSE,fig.width = 10,fig.height = 6, warning=FALSE, dev='svg'}

# SpatialFeaturePlot(object = spat_merge_log_norm,features ="Doc2g")
# SpatialFeaturePlot(object = spat_merge_log_norm,features ="Doc2g",max.cutoff = 3.2)
# SpatialFeaturePlot(object = spat_merge_log_norm,features ="Doc2g",max.cutoff = 'q95')

```

2,4/Slc20a1

```{r 018,  message=FALSE, echo=FALSE,fig.width = 10,fig.height = 6, warning=FALSE, dev='svg'}

# SpatialFeaturePlot(object = spat_merge_log_norm,features ="Slc20a1")
# SpatialFeaturePlot(object = spat_merge_log_norm,features ="Slc20a1",max.cutoff = 2.4)
# SpatialFeaturePlot(object = spat_merge_log_norm,features ="Slc20a1",max.cutoff = 'q95')

```

cutoff 2,9/Necab2

```{r 019,  message=FALSE, echo=FALSE,fig.width = 10,fig.height = 6, warning=FALSE, dev='svg'}

# SpatialFeaturePlot(object = spat_merge_log_norm,features ="Necab2")
# SpatialFeaturePlot(object = spat_merge_log_norm,features ="Necab2",max.cutoff = 2.9)
# SpatialFeaturePlot(object = spat_merge_log_norm,features ="Necab2",max.cutoff = 'q95')

```

cutoff 1,8/Doc2b

```{r 020,  message=FALSE, echo=FALSE,fig.width = 10,fig.height = 6, warning=FALSE, dev='svg'}

# SpatialFeaturePlot(object = spat_merge_log_norm,features ="Doc2b")
# SpatialFeaturePlot(object = spat_merge_log_norm,features ="Doc2b",max.cutoff = 1.8)
# SpatialFeaturePlot(object = spat_merge_log_norm,features ="Doc2b",max.cutoff = 'q95')

```


# Figure S8C

2/Elp3

```{r 021,  message=FALSE, echo=FALSE,fig.width = 10,fig.height = 6, warning=FALSE, dev='svg'}

SpatialFeaturePlot(object = spat_merge_log_norm,features ="Elp3")
SpatialFeaturePlot(object = spat_merge_log_norm,features ="Elp3",max.cutoff = 2)
SpatialFeaturePlot(object = spat_merge_log_norm,features ="Elp3",max.cutoff = 'q95')

```

1,3/Nr4a3

```{r 022,  message=FALSE, echo=FALSE,fig.width = 10,fig.height = 6, warning=FALSE, dev='svg'}

SpatialFeaturePlot(object = spat_merge_log_norm,features ="Nr4a3")
SpatialFeaturePlot(object = spat_merge_log_norm,features ="Nr4a3",max.cutoff = 1.3)
SpatialFeaturePlot(object = spat_merge_log_norm,features ="Nr4a3",max.cutoff = 'q95')

```

2,5/Klf9

```{r 023,  message=FALSE, echo=FALSE,fig.width = 10,fig.height = 6, warning=FALSE, dev='svg'}

SpatialFeaturePlot(object = spat_merge_log_norm,features ="Klf9")
SpatialFeaturePlot(object = spat_merge_log_norm,features ="Klf9",max.cutoff = 2.5)
SpatialFeaturePlot(object = spat_merge_log_norm,features ="Klf9",max.cutoff = 'q95')

```

2/Egr1

```{r 024,  message=FALSE, echo=FALSE,fig.width = 10,fig.height = 6, warning=FALSE, dev='svg'}

SpatialFeaturePlot(object = spat_merge_log_norm,features ="Egr1")
SpatialFeaturePlot(object = spat_merge_log_norm,features ="Egr1",max.cutoff = 2)
SpatialFeaturePlot(object = spat_merge_log_norm,features ="Egr1",max.cutoff = 'q95')

```


