---
title: "DGE_MothervsVirgin"
output: html_document
params:

  
  
 
  
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r 002, librarys, data loading, message=FALSE,,echo=FALSE}

library(Seurat)
#library(SeuratData)
library(ggplot2)
library(patchwork)
library(dplyr)
library(rmarkdown)
library(ggrepel)


```

# Load merged data from 1_Normalisation_subset_merge.Rmd

```{r 003, data loading, message=FALSE,echo=FALSE}
# load lognormalised data form 1_Normalisation_subset_merge.Rmd

#load("spat_merge_all_lognorm.RData")

```



# NormalizeData on Spatial assay
For DGE it is recommended to log normalisze the data (stand 2021)
```{r 004, barcode_dataFrame,  message=FALSE, echo=FALSE,width = 10,fig.height = 8}
# #Test<-spat.merge.all
# DefaultAssay(spat.merge.all) <- "Spatial"
# spat_merge_log_norm <- NormalizeData(spat.merge.all,assay = "Spatial", verbose = FALSE)
# ScaleData(spat_merge_log_norm)
# ###################################################################################
barcode_df <- FetchData(spat_merge_log_norm, vars = c("ident","orig.ident"))
barcode_df$barcode <- rownames(barcode_df)
```

# Table 1 Table1_DEG_analysis_WholeBulb

## Table 1 tab 1 Perinatal vs Virgins

B2mother20 vs (A2virgin20& C2virgin30)
csv=B2Mother20_vsA2C2virgin

```{r 005,  message=FALSE, echo=FALSE,width = 10,fig.height = 8}

cellsB2 <- barcode_df %>%
    filter(orig.ident == "B2_OB_mother20") %>%
    pull(barcode)
cells_A2_C2 <- barcode_df %>%
    filter(orig.ident == "A2_OB_virgin20" | orig.ident == "C2_OB_virgin30") %>%
    pull(barcode)
B2Mother20_vsA2C2virgin<- FindMarkers(spat_merge_log_norm, assay = "Spatial", ident.1 = cellsB2, ident.2 =cells_A2_C2 ,logfc.threshold = 0)



B2Mother20_vsA2C2virgin$Genes <- rownames(B2Mother20_vsA2C2virgin)
B2Mother20_vsA2C2virgin$diffexpressed <- "NO"
B2Mother20_vsA2C2virgin$diffexpressed[B2Mother20_vsA2C2virgin$avg_log2FC > 0.25 & B2Mother20_vsA2C2virgin$p_val_adj < 0.05] <- "Up_B2mother"
B2Mother20_vsA2C2virgin$diffexpressed[B2Mother20_vsA2C2virgin$avg_log2FC < -0.25 & B2Mother20_vsA2C2virgin$p_val_adj < 0.05] <- "Up_A2C2virgin"
B2Mother20_vsA2C2virgin$delabel <- NA
B2Mother20_vsA2C2virgin$delabel[B2Mother20_vsA2C2virgin$diffexpressed != "NO"] <- B2Mother20_vsA2C2virgin$Genes[B2Mother20_vsA2C2virgin$diffexpressed != "NO"]

# p_B2Mother20_vsA2C2virgin <- ggplot(data=B2Mother20_vsA2C2virgin, aes(x=avg_log2FC, y=-log10(p_val_adj),col=diffexpressed,label=delabel)) + geom_point()+ theme_minimal()+
#   geom_vline(xintercept=c(-0.5, 0.5), col="red")+
#   geom_hline(yintercept=-log10(0.05), col="red")+
#   scale_color_manual(values=c("black", "blue", "red"))+
#   geom_text_repel()
# p_B2Mother20_vsA2C2virgin

paged_table(B2Mother20_vsA2C2virgin, options = list(rows.print = 15, cols.print = 5))
B2Mother20_vsA2C2virgin<-B2Mother20_vsA2C2virgin[order(B2Mother20_vsA2C2virgin$p_val_adj),]

# write.csv(B2Mother20_vsA2C2virgin, "B2Mother20_vsA2C2virgin.csv")

```


## Table 1 tab 2 Perinatal vs Peri-weaning

B2mother vs  D2mother 
csv=B2mother20vsD2mother30


```{r 006,  message=FALSE, echo=FALSE,width = 10,fig.height = 8}
cellsB2 <- barcode_df %>%
    filter(orig.ident == "B2_OB_mother20") %>%
#    filter(ident == "2") %>%
    pull(barcode)
cellsD2 <- barcode_df %>%
    filter(orig.ident == "D2_OB_mother30") %>%
#   filter(ident == c("2")) %>%
    pull(barcode)


B2mother20_D2mother30<-FindMarkers(spat_merge_log_norm, assay = "Spatial", ident.1 = cellsB2, ident.2 = cellsD2 ,logfc.threshold = 0)



B2mother20_D2mother30$Genes <- rownames(B2mother20_D2mother30)
B2mother20_D2mother30$diffexpressed <- "NO"
B2mother20_D2mother30$diffexpressed[B2mother20_D2mother30$avg_log2FC > 0.25 & B2mother20_D2mother30$p_val_adj < 0.05] <- "Up_B2mother20"
B2mother20_D2mother30$diffexpressed[B2mother20_D2mother30$avg_log2FC < -0.25 & B2mother20_D2mother30$p_val_adj < 0.05] <- "Up_D2mother30"
B2mother20_D2mother30$delabel <- NA
B2mother20_D2mother30$delabel[B2mother20_D2mother30$diffexpressed != "NO"] <- B2mother20_D2mother30$Genes[B2mother20_D2mother30$diffexpressed != "NO"]

# p_B2mother20_D2mother30 <- ggplot(data=B2mother20_D2mother30, aes(x=avg_log2FC, y=-log10(p_val_adj),col=diffexpressed,label=delabel)) + geom_point()+ theme_minimal()+
#   geom_vline(xintercept=c(-0.5, 0.5), col="red")+
#   geom_hline(yintercept=-log10(0.05), col="red")+
#   scale_color_manual(values=c("black", "blue", "red"))+
#   geom_text_repel()
# p_B2mother20_D2mother30

paged_table(B2mother20_D2mother30, options = list(rows.print = 15, cols.print = 5))
B2mother20_D2mother30<-B2mother20_D2mother30[order(B2mother20_D2mother30$p_val_adj),]
# 
# write.csv(B2mother20_D2mother30, "B2mother20_D2mother30.csv")
```

# Table3_DEG_analysis_Cluster_based


## Tab 1 Perinatal vs Virgins

B2mother vs (A2 and C2 virgin)

## Cluster3 (DeepGCL)

csv=B2_A2C2deep

```{r 007,  message=FALSE, echo=FALSE,width = 10,fig.height = 8}
cellsB2c3 <- barcode_df %>%
    filter(orig.ident == "B2_OB_mother20") %>%
    filter(ident == "3") %>%
    pull(barcode)
cellsA2C2c3 <- barcode_df %>%
    filter(orig.ident == "A2_OB_virgin20" | orig.ident == "C2_OB_virgin30") %>%
    filter(ident == c("3")) %>%
    pull(barcode)


B2_A2C2deep<-FindMarkers(spat_merge_log_norm, assay = "Spatial", ident.1 = cellsB2c3, ident.2 = cellsA2C2c3 ,logfc.threshold = 0.25)



B2_A2C2deep$Genes <- rownames(B2_A2C2deep)
B2_A2C2deep$diffexpressed <- "NO"
B2_A2C2deep$diffexpressed[B2_A2C2deep$avg_log2FC > 0.25 & B2_A2C2deep$p_val_adj < 0.05] <- "Up_cluster3mother"
B2_A2C2deep$diffexpressed[B2_A2C2deep$avg_log2FC < -0.25 & B2_A2C2deep$p_val_adj < 0.05] <- "Up_cluster3virgin"
B2_A2C2deep$delabel <- NA
B2_A2C2deep$delabel[B2_A2C2deep$diffexpressed != "NO"] <- B2_A2C2deep$Genes[B2_A2C2deep$diffexpressed != "NO"]

# p_B2_A2C2deep <- ggplot(data=B2_A2C2deep, aes(x=avg_log2FC, y=-log10(p_val_adj),col=diffexpressed,label=delabel)) + geom_point()+ theme_minimal()+
#   geom_vline(xintercept=c(-0.5, 0.5), col="red")+
#   geom_hline(yintercept=-log10(0.05), col="red")+
#   scale_color_manual(values=c("black", "blue", "red"))+
#   geom_text_repel()
# p_B2_A2C2deep

paged_table(B2_A2C2deep, options = list(rows.print = 15, cols.print = 5))
B2_A2C2deep<-B2_A2C2deep[order(B2_A2C2deep$p_val_adj),]

# write.csv(B2_A2C2deep, "B2_A2C2deep.csv")
```


## Cluster2 (SupGCL)

csv=B2_A2C2superficial

```{r 008,  message=FALSE, echo=FALSE,width = 10,fig.height = 8}
cellsB2c2 <- barcode_df %>%
    filter(orig.ident == "B2_OB_mother20") %>%
    filter(ident == "2") %>%
    pull(barcode)
cellsA2C2c2 <- barcode_df %>%
    filter(orig.ident == "A2_OB_virgin20" | orig.ident == "C2_OB_virgin30") %>%
    filter(ident == c("2")) %>%
    pull(barcode)


B2_A2C2superficial<-FindMarkers(spat_merge_log_norm, assay = "Spatial", ident.1 = cellsB2c2, ident.2 = cellsA2C2c2 ,logfc.threshold = 0.25)



B2_A2C2superficial$Genes <- rownames(B2_A2C2superficial)
B2_A2C2superficial$diffexpressed <- "NO"
B2_A2C2superficial$diffexpressed[B2_A2C2superficial$avg_log2FC > 0.25 & B2_A2C2superficial$p_val_adj < 0.05] <- "Up_cluster3mother"
B2_A2C2superficial$diffexpressed[B2_A2C2superficial$avg_log2FC < -0.25 & B2_A2C2superficial$p_val_adj < 0.05] <- "Up_cluster3virgin"
B2_A2C2superficial$delabel <- NA
B2_A2C2superficial$delabel[B2_A2C2superficial$diffexpressed != "NO"] <- B2_A2C2superficial$Genes[B2_A2C2superficial$diffexpressed != "NO"]

# p_B2_A2C2superficial <- ggplot(data=B2_A2C2superficial, aes(x=avg_log2FC, y=-log10(p_val_adj),col=diffexpressed,label=delabel)) + geom_point()+ theme_minimal()+
#   geom_vline(xintercept=c(-0.5, 0.5), col="red")+
#   geom_hline(yintercept=-log10(0.05), col="red")+
#   scale_color_manual(values=c("black", "blue", "red"))+
#   geom_text_repel()
# p_B2_A2C2superficial

paged_table(B2_A2C2superficial, options = list(rows.print = 15, cols.print = 5))
B2_A2C2superficial<-B2_A2C2superficial[order(B2_A2C2superficial$p_val_adj),]

# write.csv(B2_A2C2superficial, "B2_A2C2superficial.csv")
```

## Clusters 0 and 6 (EPL)

csv=B2_A2C2ELP

```{r 009,  message=FALSE, echo=FALSE,width = 10,fig.height = 8}
cellsB2c06 <- barcode_df %>%
    filter(orig.ident == "B2_OB_mother20") %>%
    filter(ident == "0" |ident == "6") %>%
    pull(barcode)
cellsA2C2c06 <- barcode_df %>%
    filter(orig.ident == "A2_OB_virgin20" | orig.ident == "C2_OB_virgin30") %>%
    filter(ident == "0" |ident == "6") %>%
    pull(barcode)


B2_A2C2ELP<-FindMarkers(spat_merge_log_norm, assay = "Spatial", ident.1 = cellsB2c06, ident.2 = cellsA2C2c06 ,logfc.threshold = 0.25)



B2_A2C2ELP$Genes <- rownames(B2_A2C2ELP)
B2_A2C2ELP$diffexpressed <- "NO"
B2_A2C2ELP$diffexpressed[B2_A2C2ELP$avg_log2FC > 0.25 & B2_A2C2ELP$p_val_adj < 0.05] <- "Up_mother"
B2_A2C2ELP$diffexpressed[B2_A2C2ELP$avg_log2FC < -0.25 & B2_A2C2ELP$p_val_adj < 0.05] <- "Up_virgin"
B2_A2C2ELP$delabel <- NA
B2_A2C2ELP$delabel[B2_A2C2ELP$diffexpressed != "NO"] <- B2_A2C2ELP$Genes[B2_A2C2ELP$diffexpressed != "NO"]

# p_B2_A2C2ELP <- ggplot(data=B2_A2C2ELP, aes(x=avg_log2FC, y=-log10(p_val_adj),col=diffexpressed,label=delabel)) + geom_point()+ theme_minimal()+
#   geom_vline(xintercept=c(-0.5, 0.5), col="red")+
#   geom_hline(yintercept=-log10(0.05), col="red")+
#   scale_color_manual(values=c("black", "blue", "red"))+
#   geom_text_repel()
# p_B2_A2C2ELP

paged_table(B2_A2C2ELP, options = list(rows.print = 15, cols.print = 5))
B2_A2C2ELP<-B2_A2C2ELP[order(B2_A2C2ELP$p_val_adj),]

# write.csv(B2_A2C2ELP, "B2_A2C2ELP.csv")
```

## Cluster1 (GL)

csv=B2_A2C2GL

```{r 010,  message=FALSE, echo=FALSE,width = 10,fig.height = 8}
cellsB2c1 <- barcode_df %>%
    filter(orig.ident == "B2_OB_mother20") %>%
    filter(ident == "1") %>%
    pull(barcode)
cellsA2C2c1 <- barcode_df %>%
    filter(orig.ident == "A2_OB_virgin20" | orig.ident == "C2_OB_virgin30") %>%
    filter(ident == c("1")) %>%
    pull(barcode)


B2_A2C2GL<-FindMarkers(spat_merge_log_norm, assay = "Spatial", ident.1 = cellsB2c1, ident.2 = cellsA2C2c1 ,logfc.threshold = 0.25)



B2_A2C2GL$Genes <- rownames(B2_A2C2GL)
B2_A2C2GL$diffexpressed <- "NO"
B2_A2C2GL$diffexpressed[B2_A2C2GL$avg_log2FC > 0.25 & B2_A2C2GL$p_val_adj < 0.05] <- "Up_mother"
B2_A2C2GL$diffexpressed[B2_A2C2GL$avg_log2FC < -0.25 & B2_A2C2GL$p_val_adj < 0.05] <- "Up_virgin"
B2_A2C2GL$delabel <- NA
B2_A2C2GL$delabel[B2_A2C2GL$diffexpressed != "NO"] <- B2_A2C2GL$Genes[B2_A2C2GL$diffexpressed != "NO"]

# p_B2_A2C2GL <- ggplot(data=B2_A2C2GL, aes(x=avg_log2FC, y=-log10(p_val_adj),col=diffexpressed,label=delabel)) + geom_point()+ theme_minimal()+
#   geom_vline(xintercept=c(-0.5, 0.5), col="red")+
#   geom_hline(yintercept=-log10(0.05), col="red")+
#   scale_color_manual(values=c("black", "blue", "red"))+
#   geom_text_repel()
# p_B2_A2C2GL

paged_table(B2_A2C2GL, options = list(rows.print = 15, cols.print = 5))
B2_A2C2GL<-B2_A2C2GL[order(B2_A2C2GL$p_val_adj),]

# write.csv(B2_A2C2GL, "B2_A2C2GL.csv")
```

## Cluster5 (MCL)

csv=B2_A2C2MCL

```{r 011,  message=FALSE, echo=FALSE,width = 10,fig.height = 8}
cellsB2c5 <- barcode_df %>%
    filter(orig.ident == "B2_OB_mother20") %>%
    filter(ident == "5") %>%
    pull(barcode)
cellsA2C2c5 <- barcode_df %>%
    filter(orig.ident == "A2_OB_virgin20" | orig.ident == "C2_OB_virgin30") %>%
    filter(ident == c("5")) %>%
    pull(barcode)


B2_A2C2MCL<-FindMarkers(spat_merge_log_norm, assay = "Spatial", ident.1 = cellsB2c5, ident.2 = cellsA2C2c5 ,logfc.threshold = 0.25)



B2_A2C2MCL$Genes <- rownames(B2_A2C2MCL)
B2_A2C2MCL$diffexpressed <- "NO"
B2_A2C2MCL$diffexpressed[B2_A2C2MCL$avg_log2FC > 0.25 & B2_A2C2MCL$p_val_adj < 0.05] <- "Up_mother"
B2_A2C2MCL$diffexpressed[B2_A2C2MCL$avg_log2FC < -0.25 & B2_A2C2MCL$p_val_adj < 0.05] <- "Up_virgin"
B2_A2C2MCL$delabel <- NA
B2_A2C2MCL$delabel[B2_A2C2MCL$diffexpressed != "NO"] <- B2_A2C2MCL$Genes[B2_A2C2MCL$diffexpressed != "NO"]

# p_B2_A2C2MCL <- ggplot(data=B2_A2C2MCL, aes(x=avg_log2FC, y=-log10(p_val_adj),col=diffexpressed,label=delabel)) + geom_point()+ theme_minimal()+
#   geom_vline(xintercept=c(-0.5, 0.5), col="red")+
#   geom_hline(yintercept=-log10(0.05), col="red")+
#   scale_color_manual(values=c("black", "blue", "red"))+
#   geom_text_repel()
# p_B2_A2C2MCL

paged_table(B2_A2C2MCL, options = list(rows.print = 15, cols.print = 5))
B2_A2C2MCL<-B2_A2C2MCL[order(B2_A2C2MCL$p_val_adj),]

# write.csv(B2_A2C2MCL, "B2_A2C2MCL.csv")

```

## Cluster7 (RMS)

csv=B2_A2C2RMS

```{r 012,  message=FALSE, echo=FALSE,width = 10,fig.height = 8}
cellsB2c7 <- barcode_df %>%
    filter(orig.ident == "B2_OB_mother20") %>%
    filter(ident == "7") %>%
    pull(barcode)
cellsA2C2c7 <- barcode_df %>%
    filter(orig.ident == "A2_OB_virgin20" | orig.ident == "C2_OB_virgin30") %>%
    filter(ident == c("7")) %>%
    pull(barcode)


B2_A2C2RMS<-FindMarkers(spat_merge_log_norm, assay = "Spatial", ident.1 = cellsB2c7, ident.2 = cellsA2C2c7 ,logfc.threshold = 0.25)



B2_A2C2RMS$Genes <- rownames(B2_A2C2RMS)
B2_A2C2RMS$diffexpressed <- "NO"
B2_A2C2RMS$diffexpressed[B2_A2C2RMS$avg_log2FC > 0.25 & B2_A2C2RMS$p_val_adj < 0.05] <- "Up_mother"
B2_A2C2RMS$diffexpressed[B2_A2C2RMS$avg_log2FC < -0.25 & B2_A2C2RMS$p_val_adj < 0.05] <- "Up_virgin"
B2_A2C2RMS$delabel <- NA
B2_A2C2RMS$delabel[B2_A2C2RMS$diffexpressed != "NO"] <- B2_A2C2RMS$Genes[B2_A2C2RMS$diffexpressed != "NO"]

# p_B2_A2C2RMS <- ggplot(data=B2_A2C2RMS, aes(x=avg_log2FC, y=-log10(p_val_adj),col=diffexpressed,label=delabel)) + geom_point()+ theme_minimal()+
#   geom_vline(xintercept=c(-0.5, 0.5), col="red")+
#   geom_hline(yintercept=-log10(0.05), col="red")+
#   scale_color_manual(values=c("black", "blue", "red"))+
#   geom_text_repel()
# p_B2_A2C2RMS

paged_table(B2_A2C2RMS, options = list(rows.print = 15, cols.print = 5))
B2_A2C2RMS<-B2_A2C2RMS[order(B2_A2C2RMS$p_val_adj),]

# write.csv(B2_A2C2RMS, "B2_A2C2RMS.csv")

```

## Cluster8 (AOB_GCL)

csv=B2_A2C2AOB

```{r 013,  message=FALSE, echo=FALSE,width = 10,fig.height = 8}
cellsB2c8 <- barcode_df %>%
    filter(orig.ident == "B2_OB_mother20") %>%
    filter(ident == "8") %>%
    pull(barcode)
cellsA2C2c8 <- barcode_df %>%
    filter(orig.ident == "A2_OB_virgin20" | orig.ident == "C2_OB_virgin30") %>%
    filter(ident == c("8")) %>%
    pull(barcode)


B2_A2C2AOB<-FindMarkers(spat_merge_log_norm, assay = "Spatial", ident.1 = cellsB2c8, ident.2 = cellsA2C2c8 ,logfc.threshold = 0.25)



B2_A2C2AOB$Genes <- rownames(B2_A2C2AOB)
B2_A2C2AOB$diffexpressed <- "NO"
B2_A2C2AOB$diffexpressed[B2_A2C2AOB$avg_log2FC > 0.25 & B2_A2C2AOB$p_val_adj < 0.05] <- "Up_mother"
B2_A2C2AOB$diffexpressed[B2_A2C2AOB$avg_log2FC < -0.25 & B2_A2C2AOB$p_val_adj < 0.05] <- "Up_virgin"
B2_A2C2AOB$delabel <- NA
B2_A2C2AOB$delabel[B2_A2C2AOB$diffexpressed != "NO"] <- B2_A2C2AOB$Genes[B2_A2C2AOB$diffexpressed != "NO"]

# p_B2_A2C2AOB <- ggplot(data=B2_A2C2AOB, aes(x=avg_log2FC, y=-log10(p_val_adj),col=diffexpressed,label=delabel)) + geom_point()+ theme_minimal()+
#   geom_vline(xintercept=c(-0.5, 0.5), col="red")+
#   geom_hline(yintercept=-log10(0.05), col="red")+
#   scale_color_manual(values=c("black", "blue", "red"))+
#   geom_text_repel()
# p_B2_A2C2AOB

paged_table(B2_A2C2AOB, options = list(rows.print = 15, cols.print = 5))
B2_A2C2AOB<-B2_A2C2AOB[order(B2_A2C2AOB$p_val_adj),]

# write.csv(B2_A2C2AOB, "B2_A2C2AOB.csv")
```



# Table3_DEG_analysis_Cluster_based


## Tab 2 Peri-weaning vs Virgins

D2mother vs (A2 and C2 virgin)

## Cluster3 (DeepGCL)

csv=D2_A2C2deep

```{r 014,  message=FALSE, echo=FALSE,width = 10,fig.height = 8}
cellsD2c3 <- barcode_df %>%
    filter(orig.ident == "D2_OB_mother30") %>%
    filter(ident == c("3")) %>%
    pull(barcode)

B2_A2C2deep<-FindMarkers(spat_merge_log_norm, assay = "Spatial", ident.1 = cellsD2c3, ident.2 = cellsA2C2c3 ,logfc.threshold = 0.25)



B2_A2C2deep$Genes <- rownames(B2_A2C2deep)
B2_A2C2deep$diffexpressed <- "NO"
B2_A2C2deep$diffexpressed[B2_A2C2deep$avg_log2FC > 0.25 & B2_A2C2deep$p_val_adj < 0.05] <- "Up_cluster3mother30"
B2_A2C2deep$diffexpressed[B2_A2C2deep$avg_log2FC < -0.25 & B2_A2C2deep$p_val_adj < 0.05] <- "Up_cluster3virgin"
B2_A2C2deep$delabel <- NA
B2_A2C2deep$delabel[B2_A2C2deep$diffexpressed != "NO"] <- B2_A2C2deep$Genes[B2_A2C2deep$diffexpressed != "NO"]

# p_B2_A2C2deep <- ggplot(data=B2_A2C2deep, aes(x=avg_log2FC, y=-log10(p_val_adj),col=diffexpressed,label=delabel)) + geom_point()+ theme_minimal()+
#   geom_vline(xintercept=c(-0.5, 0.5), col="red")+
#   geom_hline(yintercept=-log10(0.05), col="red")+
#   scale_color_manual(values=c("black", "blue", "red"))+
#   geom_text_repel()
# p_B2_A2C2deep

paged_table(B2_A2C2deep, options = list(rows.print = 15, cols.print = 5))
B2_A2C2deep<-B2_A2C2deep[order(B2_A2C2deep$p_val_adj),]

# write.csv(B2_A2C2deep, "D2_A2C2deep.csv")

```

## Cluster2 (SupGCL)

csv=D2_A2C2superficial

```{r 015,  message=FALSE, echo=FALSE,width = 10,fig.height = 8}
cellsD2c2 <- barcode_df %>%
    filter(orig.ident == "D2_OB_mother30") %>%
    filter(ident == c("2")) %>%
    pull(barcode)


D2_A2C2superficial<-FindMarkers(spat_merge_log_norm, assay = "Spatial", ident.1 = cellsD2c2, ident.2 = cellsA2C2c2 ,logfc.threshold = 0.25)



D2_A2C2superficial$Genes <- rownames(D2_A2C2superficial)
D2_A2C2superficial$diffexpressed <- "NO"
D2_A2C2superficial$diffexpressed[D2_A2C2superficial$avg_log2FC > 0.25 & D2_A2C2superficial$p_val_adj < 0.05] <- "Up_cluster3mother30"
D2_A2C2superficial$diffexpressed[D2_A2C2superficial$avg_log2FC < -0.25 & D2_A2C2superficial$p_val_adj < 0.05] <- "Up_cluster3virgin"
D2_A2C2superficial$delabel <- NA
D2_A2C2superficial$delabel[D2_A2C2superficial$diffexpressed != "NO"] <- D2_A2C2superficial$Genes[D2_A2C2superficial$diffexpressed != "NO"]

# p_D2_A2C2superficial <- ggplot(data=D2_A2C2superficial, aes(x=avg_log2FC, y=-log10(p_val_adj),col=diffexpressed,label=delabel)) + geom_point()+ theme_minimal()+
#   geom_vline(xintercept=c(-0.5, 0.5), col="red")+
#   geom_hline(yintercept=-log10(0.05), col="red")+
#   scale_color_manual(values=c("black", "blue", "red"))+
#   geom_text_repel()
# p_D2_A2C2superficial

paged_table(D2_A2C2superficial, options = list(rows.print = 15, cols.print = 5))
D2_A2C2superficial<-D2_A2C2superficial[order(D2_A2C2superficial$p_val_adj),]

# write.csv(D2_A2C2superficial, "D2_A2C2superficial.csv")

```


## Clusters 0 and 6 (EPL)

csv=D2_A2C2EPL

```{r 016,  message=FALSE, echo=FALSE,width = 10,fig.height = 8}
cellsD2c06 <- barcode_df %>%
    filter(orig.ident == "D2_OB_mother30") %>%
    filter(ident == "0" |ident == "6") %>%
    pull(barcode)


D2_A2C2EPL<-FindMarkers(spat_merge_log_norm, assay = "Spatial", ident.1 = cellsD2c06, ident.2 = cellsA2C2c06 ,logfc.threshold = 0.25)



D2_A2C2EPL$Genes <- rownames(D2_A2C2EPL)
D2_A2C2EPL$diffexpressed <- "NO"
D2_A2C2EPL$diffexpressed[D2_A2C2EPL$avg_log2FC > 0.25 & D2_A2C2EPL$p_val_adj < 0.05] <- "Up_mother"
D2_A2C2EPL$diffexpressed[D2_A2C2EPL$avg_log2FC < -0.25 & D2_A2C2EPL$p_val_adj < 0.05] <- "Up_virgin"
D2_A2C2EPL$delabel <- NA
D2_A2C2EPL$delabel[D2_A2C2EPL$diffexpressed != "NO"] <- D2_A2C2EPL$Genes[D2_A2C2EPL$diffexpressed != "NO"]

# p_D2_A2C2EPL <- ggplot(data=D2_A2C2EPL, aes(x=avg_log2FC, y=-log10(p_val_adj),col=diffexpressed,label=delabel)) + geom_point()+ theme_minimal()+
#   geom_vline(xintercept=c(-0.5, 0.5), col="red")+
#   geom_hline(yintercept=-log10(0.05), col="red")+
#   scale_color_manual(values=c("black", "blue", "red"))+
#   geom_text_repel()
# p_D2_A2C2EPL

paged_table(D2_A2C2EPL, options = list(rows.print = 15, cols.print = 5))
D2_A2C2EPL<-D2_A2C2EPL[order(D2_A2C2EPL$p_val_adj),]

# write.csv(D2_A2C2EPL, "D2_A2C2EPL.csv")
```

## Cluster1 (GL)

csv=D2_A2C2GL

```{r 017,  message=FALSE, echo=FALSE,width = 10,fig.height = 8}
cellsD2c1 <- barcode_df %>%
    filter(orig.ident == "D2_OB_mother30") %>%
    filter(ident == "1") %>%
    pull(barcode)


D2_A2C2GL<-FindMarkers(spat_merge_log_norm, assay = "Spatial", ident.1 = cellsD2c1, ident.2 = cellsA2C2c1 ,logfc.threshold = 0.25)



D2_A2C2GL$Genes <- rownames(D2_A2C2GL)
D2_A2C2GL$diffexpressed <- "NO"
D2_A2C2GL$diffexpressed[D2_A2C2GL$avg_log2FC > 0.25 & D2_A2C2GL$p_val_adj < 0.05] <- "Up_mother"
D2_A2C2GL$diffexpressed[D2_A2C2GL$avg_log2FC < -0.25 & D2_A2C2GL$p_val_adj < 0.05] <- "Up_virgin"
D2_A2C2GL$delabel <- NA
D2_A2C2GL$delabel[D2_A2C2GL$diffexpressed != "NO"] <- D2_A2C2GL$Genes[D2_A2C2GL$diffexpressed != "NO"]

# p_D2_A2C2GL <- ggplot(data=D2_A2C2GL, aes(x=avg_log2FC, y=-log10(p_val_adj),col=diffexpressed,label=delabel)) + geom_point()+ theme_minimal()+
#   geom_vline(xintercept=c(-0.5, 0.5), col="red")+
#   geom_hline(yintercept=-log10(0.05), col="red")+
#   scale_color_manual(values=c("black", "blue", "red"))+
#   geom_text_repel()
# p_D2_A2C2GL

paged_table(D2_A2C2GL, options = list(rows.print = 15, cols.print = 5))
D2_A2C2GL<-D2_A2C2GL[order(D2_A2C2GL$p_val_adj),]

# write.csv(D2_A2C2GL, "D2_A2C2GL.csv")

```

## Cluster5 (MCL)

csv=D2_A2C2MCL

```{r 018,  message=FALSE, echo=FALSE,width = 10,fig.height = 8}
cellsD2c5 <- barcode_df %>%
    filter(orig.ident == "D2_OB_mother30") %>%
    filter(ident == "5") %>%
    pull(barcode)


D2_A2C2MCL<-FindMarkers(spat_merge_log_norm, assay = "Spatial", ident.1 = cellsD2c5, ident.2 = cellsA2C2c5 ,logfc.threshold = 0.25)



D2_A2C2MCL$Genes <- rownames(D2_A2C2MCL)
D2_A2C2MCL$diffexpressed <- "NO"
D2_A2C2MCL$diffexpressed[D2_A2C2MCL$avg_log2FC > 0.25 & D2_A2C2MCL$p_val_adj < 0.05] <- "Up_mother"
D2_A2C2MCL$diffexpressed[D2_A2C2MCL$avg_log2FC < -0.25 & D2_A2C2MCL$p_val_adj < 0.05] <- "Up_virgin"
D2_A2C2MCL$delabel <- NA
D2_A2C2MCL$delabel[D2_A2C2MCL$diffexpressed != "NO"] <- D2_A2C2MCL$Genes[D2_A2C2MCL$diffexpressed != "NO"]

# p_D2_A2C2MCL <- ggplot(data=D2_A2C2MCL, aes(x=avg_log2FC, y=-log10(p_val_adj),col=diffexpressed,label=delabel)) + geom_point()+ theme_minimal()+
#   geom_vline(xintercept=c(-0.5, 0.5), col="red")+
#   geom_hline(yintercept=-log10(0.05), col="red")+
#   scale_color_manual(values=c("black", "blue", "red"))+
#   geom_text_repel()
# p_D2_A2C2MCL

paged_table(D2_A2C2MCL, options = list(rows.print = 15, cols.print = 5))
D2_A2C2MCL<-D2_A2C2MCL[order(D2_A2C2MCL$p_val_adj),]

# write.csv(D2_A2C2MCL, "D2_A2C2MCL.csv")

```

## Cluster7 (RMS)
csv=D2_A2C2RMS


```{r 019,  message=FALSE, echo=FALSE,width = 10,fig.height = 8}
cellsD2c7 <- barcode_df %>%
    filter(orig.ident == "D2_OB_mother30") %>%
    filter(ident == "7") %>%
    pull(barcode)



D2_A2C2RMS<-FindMarkers(spat_merge_log_norm, assay = "Spatial", ident.1 = cellsD2c7, ident.2 = cellsA2C2c7 ,logfc.threshold = 0.25)



D2_A2C2RMS$Genes <- rownames(D2_A2C2RMS)
D2_A2C2RMS$diffexpressed <- "NO"
D2_A2C2RMS$diffexpressed[D2_A2C2RMS$avg_log2FC > 0.25 & D2_A2C2RMS$p_val_adj < 0.05] <- "Up_mother"
D2_A2C2RMS$diffexpressed[D2_A2C2RMS$avg_log2FC < -0.25 & D2_A2C2RMS$p_val_adj < 0.05] <- "Up_virgin"
D2_A2C2RMS$delabel <- NA
D2_A2C2RMS$delabel[D2_A2C2RMS$diffexpressed != "NO"] <- D2_A2C2RMS$Genes[D2_A2C2RMS$diffexpressed != "NO"]

# p_D2_A2C2RMS <- ggplot(data=D2_A2C2RMS, aes(x=avg_log2FC, y=-log10(p_val_adj),col=diffexpressed,label=delabel)) + geom_point()+ theme_minimal()+
#   geom_vline(xintercept=c(-0.5, 0.5), col="red")+
#   geom_hline(yintercept=-log10(0.05), col="red")+
#   scale_color_manual(values=c("black", "blue", "red"))+
#   geom_text_repel()
# p_D2_A2C2RMS

paged_table(D2_A2C2RMS, options = list(rows.print = 15, cols.print = 5))
D2_A2C2RMS<-D2_A2C2RMS[order(D2_A2C2RMS$p_val_adj),]

# write.csv(D2_A2C2RMS, "D2_A2C2RMS.csv")

```

## Cluster8 (AOB_GCL)

csv=D2_A2C2AOB

```{r 020,  message=FALSE, echo=FALSE,width = 10,fig.height = 8}
cellsD2c8 <- barcode_df %>%
    filter(orig.ident == "D2_OB_mother30") %>%
    filter(ident == "8") %>%
    pull(barcode)


D2_A2C2AOB<-FindMarkers(spat_merge_log_norm, assay = "Spatial", ident.1 = cellsD2c8, ident.2 = cellsA2C2c8 ,logfc.threshold = 0.25)



D2_A2C2AOB$Genes <- rownames(D2_A2C2AOB)
D2_A2C2AOB$diffexpressed <- "NO"
D2_A2C2AOB$diffexpressed[D2_A2C2AOB$avg_log2FC > 0.25 & D2_A2C2AOB$p_val_adj < 0.05] <- "Up_mother"
D2_A2C2AOB$diffexpressed[D2_A2C2AOB$avg_log2FC < -0.25 & D2_A2C2AOB$p_val_adj < 0.05] <- "Up_virgin"
D2_A2C2AOB$delabel <- NA
D2_A2C2AOB$delabel[D2_A2C2AOB$diffexpressed != "NO"] <- D2_A2C2AOB$Genes[D2_A2C2AOB$diffexpressed != "NO"]

# p_D2_A2C2AOB <- ggplot(data=D2_A2C2AOB, aes(x=avg_log2FC, y=-log10(p_val_adj),col=diffexpressed,label=delabel)) + geom_point()+ theme_minimal()+
#   geom_vline(xintercept=c(-0.5, 0.5), col="red")+
#   geom_hline(yintercept=-log10(0.05), col="red")+
#   scale_color_manual(values=c("black", "blue", "red"))+
#   geom_text_repel()
# p_D2_A2C2AOB

paged_table(D2_A2C2AOB, options = list(rows.print = 15, cols.print = 5))
D2_A2C2AOB<-D2_A2C2AOB[order(D2_A2C2AOB$p_val_adj),]

# write.csv(D2_A2C2AOB, "D2_A2C2AOB.csv")

```

# Table3_DEG_analysis_Cluster_based


## Tab 3 C4_C9_PerinatalCare

## Cluster4
!general:
```{r 021,  message=FALSE, echo=FALSE,width = 10,fig.height = 8}
cluster4<-FindMarkers(spat_merge_log_norm, assay = "Spatial", ident.1 = "4", ident.2 = NULL ,logfc.threshold = 0.25, only.pos = TRUE)


cluster4$Genes <- rownames(cluster4)
cluster4$diffexpressed <- "NO"
cluster4$diffexpressed[cluster4$avg_log2FC > 0.25 & cluster4$p_val_adj < 0.05] <- "Up_cluster4"
cluster4$delabel <- NA
cluster4$delabel[cluster4$diffexpressed != "NO"] <- cluster4$Genes[cluster4$diffexpressed != "NO"]

# p_cluster4 <- ggplot(data=cluster4, aes(x=avg_log2FC, y=-log10(p_val_adj),col=diffexpressed,label=delabel)) + geom_point()+ theme_minimal()+
#   geom_vline(xintercept=c(0.5), col="red")+
#   geom_hline(yintercept=-log10(0.05), col="red")+
#   scale_color_manual(values=c("black", "blue", "red"))+
#   geom_text_repel()
# p_cluster4

cluster4<- cluster4[order(cluster4$p_val_adj),]
paged_table(cluster4, options = list(rows.print = 15, cols.print = 5))

# write.csv(cluster4, "cluster4.csv")
```


## Cluster4

csv=B2_cluster4

```{r 022,  message=FALSE, echo=FALSE,width = 10,fig.height = 8}
cellsB2c4 <- barcode_df %>%
    filter(orig.ident == "B2_OB_mother20") %>%
    filter(ident == "4") %>%
    pull(barcode)



B2_cluster4<-FindMarkers(spat_merge_log_norm, assay = "Spatial", ident.1 = cellsB2c4, ident.2 = NULL ,logfc.threshold = 0.25, only.pos = TRUE)



B2_cluster4$Genes <- rownames(B2_cluster4)
B2_cluster4$diffexpressed <- "NO"
B2_cluster4$diffexpressed[B2_cluster4$avg_log2FC > 0.25 & B2_cluster4$p_val_adj < 0.05] <- "Up_B2_cluster4"
B2_cluster4$delabel <- NA
B2_cluster4$delabel[B2_cluster4$diffexpressed != "NO"] <- B2_cluster4$Genes[B2_cluster4$diffexpressed != "NO"]

# p_B2_cluster4 <- ggplot(data=B2_cluster4, aes(x=avg_log2FC, y=-log10(p_val_adj),col=diffexpressed,label=delabel)) + geom_point()+ theme_minimal()+
#   geom_vline(xintercept=c(0.5), col="red")+
#   geom_hline(yintercept=-log10(0.05), col="red")+
#   scale_color_manual(values=c("black", "blue", "red"))+
#   geom_text_repel()
# p_B2_cluster4

B2_cluster4<- B2_cluster4[order(B2_cluster4$p_val_adj),]
paged_table(B2_cluster4, options = list(rows.print = 15, cols.print = 5))

# write.csv(B2_cluster4, "B2_cluster4.csv")
```

## Cluster4 logfold 0
csv=B2_cluster4

```{r 022a,  message=FALSE, echo=FALSE,width = 10,fig.height = 8}


B2_cluster4_logfold0<-FindMarkers(spat_merge_log_norm, assay = "Spatial", ident.1 = cellsB2c4, ident.2 = NULL ,logfc.threshold = 0, only.pos = TRUE)



B2_cluster4_logfold0$Genes <- rownames(B2_cluster4_logfold0)
B2_cluster4_logfold0$diffexpressed <- "NO"
B2_cluster4_logfold0$diffexpressed[B2_cluster4_logfold0$avg_log2FC > 0.25 & B2_cluster4_logfold0$p_val_adj < 0.05] <- "Up_B2_cluster4_logfold0"
B2_cluster4_logfold0$delabel <- NA
B2_cluster4_logfold0$delabel[B2_cluster4_logfold0$diffexpressed != "NO"] <- B2_cluster4_logfold0$Genes[B2_cluster4_logfold0$diffexpressed != "NO"]

p_B2_cluster4_logfold0 <- ggplot(data=B2_cluster4_logfold0, aes(x=avg_log2FC, y=-log10(p_val_adj),col=diffexpressed,label=delabel)) + geom_point()+ theme_minimal()+
  geom_vline(xintercept=c(0.5), col="red")+
  geom_hline(yintercept=-log10(0.05), col="red")+
  scale_color_manual(values=c("black", "blue", "red"))+
  geom_text_repel()
p_B2_cluster4_logfold0

B2_cluster4_logfold0<- B2_cluster4_logfold0[order(B2_cluster4_logfold0$p_val_adj),]
paged_table(B2_cluster4_logfold0, options = list(rows.print = 15, cols.print = 5))

# write.csv(B2_cluster4_logfold0, "/media/Jonas_Kretz/Visium_gene_expression/Visium_mouse_brain/Analysis_mouse_brain/Workflow_sct_merge_log/Rmd_and_data/processed_data/DGE_csv/B2_cluster4_logfold0.csv")
```





## Cluster9

!general:

csv=cluster9
```{r 023,  message=FALSE, echo=FALSE,width = 10,fig.height = 8}
cluster9<-FindMarkers(spat_merge_log_norm, assay = "Spatial", ident.1 = "9", ident.2 = NULL ,logfc.threshold = 0.25, only.pos = TRUE)


cluster9$Genes <- rownames(cluster9)
cluster9$diffexpressed <- "NO"
cluster9$diffexpressed[cluster9$avg_log2FC > 0.25 & cluster9$p_val_adj < 0.05] <- "Up_cluster9"
cluster9$delabel <- NA
cluster9$delabel[cluster9$diffexpressed != "NO"] <- cluster9$Genes[cluster9$diffexpressed != "NO"]

# p_cluster9 <- ggplot(data=cluster9, aes(x=avg_log2FC, y=-log10(p_val_adj),col=diffexpressed,label=delabel)) + geom_point()+ theme_minimal()+
#   geom_vline(xintercept=c(0.5), col="red")+
#   geom_hline(yintercept=-log10(0.05), col="red")+
#   scale_color_manual(values=c("black", "blue", "red"))+
#   geom_text_repel()
# p_cluster9

cluster9<- cluster9[order(cluster9$p_val_adj),]
paged_table(cluster9, options = list(rows.print = 15, cols.print = 5))

# write.csv(cluster9, "cluster9.csv")
```

## Cluster9


csv=B2_cluster9

```{r 024,  message=FALSE, echo=FALSE,width = 10,fig.height = 8}
cellsB2c9 <- barcode_df %>%
    filter(orig.ident == "B2_OB_mother20") %>%
    filter(ident == "9") %>%
    pull(barcode)



B2_cluster9<-FindMarkers(spat_merge_log_norm, assay = "Spatial", ident.1 = cellsB2c9, ident.2 = NULL ,logfc.threshold = 0.25, only.pos = TRUE)



B2_cluster9$Genes <- rownames(B2_cluster9)
B2_cluster9$diffexpressed <- "NO"
B2_cluster9$diffexpressed[B2_cluster9$avg_log2FC > 0.25 & B2_cluster9$p_val_adj < 0.05] <- "Up_B2_cluster9"
B2_cluster9$delabel <- NA
B2_cluster9$delabel[B2_cluster9$diffexpressed != "NO"] <- B2_cluster9$Genes[B2_cluster9$diffexpressed != "NO"]

# p_B2_cluster9 <- ggplot(data=B2_cluster9, aes(x=avg_log2FC, y=-log10(p_val_adj),col=diffexpressed,label=delabel)) + geom_point()+ theme_minimal()+
#   geom_vline(xintercept=c(0.5), col="red")+
#   geom_hline(yintercept=-log10(0.05), col="red")+
#   scale_color_manual(values=c("black", "blue", "red"))+
#   geom_text_repel()
# p_B2_cluster9

B2_cluster9<- B2_cluster9[order(B2_cluster9$p_val_adj),]
paged_table(B2_cluster9, options = list(rows.print = 15, cols.print = 5))

# write.csv(B2_cluster9, "B2_cluster9.csv")
```

## Cluster9


csv=B2_cluster9

```{r 024a,  message=FALSE, echo=FALSE,width = 10,fig.height = 8}
cellsB2c9 <- barcode_df %>%
    filter(orig.ident == "B2_OB_mother20") %>%
    filter(ident == "9") %>%
    pull(barcode)



B2_cluster9<-FindMarkers(spat_merge_log_norm, assay = "Spatial", ident.1 = cellsB2c9, ident.2 = NULL ,logfc.threshold = 0.25, only.pos = TRUE)



B2_cluster9$Genes <- rownames(B2_cluster9)
B2_cluster9$diffexpressed <- "NO"
B2_cluster9$diffexpressed[B2_cluster9$avg_log2FC > 0.25 & B2_cluster9$p_val_adj < 0.05] <- "Up_B2_cluster9"
B2_cluster9$delabel <- NA
B2_cluster9$delabel[B2_cluster9$diffexpressed != "NO"] <- B2_cluster9$Genes[B2_cluster9$diffexpressed != "NO"]

# p_B2_cluster9 <- ggplot(data=B2_cluster9, aes(x=avg_log2FC, y=-log10(p_val_adj),col=diffexpressed,label=delabel)) + geom_point()+ theme_minimal()+
#   geom_vline(xintercept=c(0.5), col="red")+
#   geom_hline(yintercept=-log10(0.05), col="red")+
#   scale_color_manual(values=c("black", "blue", "red"))+
#   geom_text_repel()
# p_B2_cluster9

B2_cluster9<- B2_cluster9[order(B2_cluster9$p_val_adj),]
paged_table(B2_cluster9, options = list(rows.print = 15, cols.print = 5))

# write.csv(B2_cluster9, "B2_cluster9.csv")
```


csv=B2_cluster9_log

```{r 024b,  message=FALSE, echo=FALSE,width = 10,fig.height = 8}
cellsB2c9 <- barcode_df %>%
    filter(orig.ident == "B2_OB_mother20") %>%
    filter(ident == "9") %>%
    pull(barcode)



B2_cluster9_logfold0<-FindMarkers(spat_merge_log_norm, assay = "Spatial", ident.1 = cellsB2c9, ident.2 = NULL ,logfc.threshold = 0, only.pos = TRUE)



B2_cluster9_logfold0$Genes <- rownames(B2_cluster9_logfold0)
B2_cluster9_logfold0$diffexpressed <- "NO"
B2_cluster9_logfold0$diffexpressed[B2_cluster9_logfold0$avg_log2FC > 0.25 & B2_cluster9_logfold0$p_val_adj < 0.05] <- "Up_B2_cluster9logfold0"
B2_cluster9_logfold0$delabel <- NA
B2_cluster9_logfold0$delabel[B2_cluster9_logfold0$diffexpressed != "NO"] <- B2_cluster9_logfold0$Genes[B2_cluster9_logfold0$diffexpressed != "NO"]

# p_B2_cluster9_logfold0 <- ggplot(data=B2_cluster9_logfold0, aes(x=avg_log2FC, y=-log10(p_val_adj),col=diffexpressed,label=delabel)) + geom_point()+ theme_minimal()+
#   geom_vline(xintercept=c(0.5), col="red")+
#   geom_hline(yintercept=-log10(0.05), col="red")+
#   scale_color_manual(values=c("black", "blue", "red"))+
#   geom_text_repel()
# p_B2_cluster9_logfold0

B2_cluster9_logfold0<- B2_cluster9_logfold0[order(B2_cluster9_logfold0$p_val_adj),]
paged_table(B2_cluster9_logfold0, options = list(rows.print = 15, cols.print = 5))

# write.csv(B2_cluster9_logfold0, "B2_cluster9_logfold0.csv")
```


## Tab 4 C4_C9_Peri-weaning

## Cluster4

csv=D2_cluster4

```{r 025,  message=FALSE, echo=FALSE,width = 10,fig.height = 8}
cellsD2c4 <- barcode_df %>%
    filter(orig.ident == "D2_OB_mother30") %>%
    filter(ident == "4") %>%
    pull(barcode)



D2_cluster4<-FindMarkers(spat_merge_log_norm, assay = "Spatial", ident.1 = cellsD2c4, ident.2 = NULL ,logfc.threshold = 0.25, only.pos = TRUE)



D2_cluster4$Genes <- rownames(D2_cluster4)
D2_cluster4$diffexpressed <- "NO"
D2_cluster4$diffexpressed[D2_cluster4$avg_log2FC > 0.25 & D2_cluster4$p_val_adj < 0.05] <- "Up_D2_cluster4"
D2_cluster4$delabel <- NA
D2_cluster4$delabel[D2_cluster4$diffexpressed != "NO"] <- D2_cluster4$Genes[D2_cluster4$diffexpressed != "NO"]

# p_D2_cluster4 <- ggplot(data=D2_cluster4, aes(x=avg_log2FC, y=-log10(p_val_adj),col=diffexpressed,label=delabel)) + geom_point()+ theme_minimal()+
#   geom_vline(xintercept=c(0.5), col="red")+
#   geom_hline(yintercept=-log10(0.05), col="red")+
#   scale_color_manual(values=c("black", "blue", "red"))+
#   geom_text_repel()
# p_D2_cluster4

D2_cluster4<- D2_cluster4[order(D2_cluster4$p_val_adj),]
paged_table(D2_cluster4, options = list(rows.print = 15, cols.print = 5))

# write.csv(D2_cluster4, "D2_cluster4.csv")
```

## Cluster9

csv=D2_cluster9

```{r 026,  message=FALSE, echo=FALSE,width = 10,fig.height = 8}
cellsD2c9 <- barcode_df %>%
    filter(orig.ident == "D2_OB_mother30") %>%
    filter(ident == "9") %>%
    pull(barcode)




D2_cluster9<-FindMarkers(spat_merge_log_norm, assay = "Spatial", ident.1 = cellsD2c9, ident.2 = NULL ,logfc.threshold = 0.25, only.pos = TRUE)



D2_cluster9$Genes <- rownames(D2_cluster9)
D2_cluster9$diffexpressed <- "NO"
D2_cluster9$diffexpressed[D2_cluster9$avg_log2FC > 0.25 & D2_cluster9$p_val_adj < 0.05] <- "Up_D2_cluster9"
D2_cluster9$delabel <- NA
D2_cluster9$delabel[D2_cluster9$diffexpressed != "NO"] <- D2_cluster9$Genes[D2_cluster9$diffexpressed != "NO"]

# p_D2_cluster9 <- ggplot(data=D2_cluster9, aes(x=avg_log2FC, y=-log10(p_val_adj),col=diffexpressed,label=delabel)) + geom_point()+ theme_minimal()+
#   geom_vline(xintercept=c(0.5), col="red")+
#   geom_hline(yintercept=-log10(0.05), col="red")+
#   scale_color_manual(values=c("black", "blue", "red"))+
#   geom_text_repel()
# p_D2_cluster9

D2_cluster9<- D2_cluster9[order(D2_cluster9$p_val_adj),]
paged_table(D2_cluster9, options = list(rows.print = 15, cols.print = 5))

# write.csv(D2_cluster9, "D2_cluster9.csv")
```

